Reconstructing Propositional Proofs in Type Theory

### 2017-12-06 paper/sections/proof-reconstruction.tex
[ paper ] more spacing in metis table/strip rule begins section.

% % ................................................

@@

In this section, we reconstruct each \Metis inference rule in
Table~\ref{tab:agda-metis-table} via a function and its respective
theorem. We present a pattern of the formal description for these
rules in Example~\ref{ex:inference-rule-pattern}.

\begin{notation}
  The function name written in \texttt{typewriter} font refers to a
  \Metis inference rule. The same function name written using
  \textsf{sans serif} font refers to our formalized version to
  reconstruct the rule and implemented in~\cite{AgdaMetis}. We use
  \Source and \Target as synonyms of the \Prop type to describe in the
  function types the role of the arguments.
\end{notation}

@@

% ------------------------------------------------------------------

\subfile{sections/proof-reconstruction/strip.tex}
\subfile{sections/proof-reconstruction/conjunct.tex}
\subfile{sections/proof-reconstruction/resolve.tex}
\subfile{sections/proof-reconstruction/canonicalize.tex}
\subfile{sections/proof-reconstruction/clausify.tex}
\subfile{sections/proof-reconstruction/simplify.tex}

>>>>

% ...................................................................

@@

In this section, we reconstruct each \Metis inference rule in
Table~\ref{tab:agda-metis-table}.
We begin describing the reconstruction of the \strip inference rule
since this rule  is the only one that closely follows the \Metis
source code. For the other rules, we present a pattern of the formal
description for these rules in
Example~\ref{ex:inference-rule-pattern} to reconstruct such rules.

\begin{notation}
  The function name written in \texttt{typewriter} font refers to a
  \Metis inference rule in the \TSTP derivations. The same function
  name written using
  \textsf{sans serif} font refers to our formalized version to
  reconstruct the rule and formally implemented in~\cite{AgdaMetis}.
  To increase the readability of our formal descriptions in
  functions and theorems, we adopt
  the convention to use \Source and \Target as synonyms of the \Prop
  type. The \Source type in the reconstructed rule definition refers
  to the argument in the \TSTP derivations, \ie the input formula of
  the inference rule. A formula of \Target type refers to the
  expected result of the rule found in the \TSTP derivation.
\end{notation}

\subfile{sections/proof-reconstruction/strip.tex}

@@

% ------------------------------------------------------------------
% Rules that follow the pattern:

\subfile{sections/proof-reconstruction/conjunct.tex}
\subfile{sections/proof-reconstruction/resolve.tex}
\subfile{sections/proof-reconstruction/canonicalize.tex}
\subfile{sections/proof-reconstruction/clausify.tex}
\subfile{sections/proof-reconstruction/simplify.tex}
